A quantitative framework for investigating the reliability of network construction

### 2018-03-08 manuscript/CI_interactions.tex
spellchecked

    Representating an assemblage of species as a network offers a convenient summary of how the community is constructed as it simultaneously accounts for species composition and interactions between species. A tabulation of the nodes (species) and their relative abundances forms the basis for traditional metrics of community composition. To move from these simpler metrics to a network framework, the tabulation of nodes is combined with interactions (links between nodes) so that networks provide additional, higher-order information on community structure. While this additional information is useful (as, for example, interactions can affect changes in species abundances over time), empirical descriptions of ecological networks are still limited because they are usually considered to be static representations of the communities and interactions they describe. That is, whether the network is assembled based on aggregated data, a single intensive ``snapshot" sample, or expert knowledge, interactions are assumed to occur deterministically wherever and whenever the community is observed~\citep{Olesen2011a}.

    The assumption of static communities contrasts significantly with the widely recognized stochasticity of ecological communities~\citep{Gotelli2000}. Community composition and species abundances vary from site to site~\citep{Baiser2012} and over time within a site~\citep{Olesen2011a}. Likewise, interactions vary over space~\citep{Kitching1987,Baiser2012}, time~\citep{Kitching1987,Olesen2011a}, and between individuals of a given species~\citep{Pires2011a,Fodrie2015,Novak2015}. Moreover, variability in community composition and interactions may or may not be closely related. The removal of a species from a site will obviously also remove its interactions but, conversely, the co-occurrence of potentially interacting species does not in itself guarantee that they will interact at a given place and time. Interactions can be lost if the interaction partners remain present but are separated in time or are too rare to detect each other~\citep{Tylianakis2010}. Interactions can also fail to occur because of environmental contingencies~\citep{Poisot2015}, or through changes to individual preferences~\citep{Fodrie2015}.

@@

    Together, the combination of these three sources of uncertainty --interaction uncertainty, process uncertainty, and detection uncertainty-- results in a range of potential explanations for the observation of an absence of interaction ($D$, $X$, and/or $L = 0$). The ecologist wanting to describe the network, however, is specifically interested in the situation where $L = 0$ (i.e., in true absences). Thus, while there is have no difficulty interpreting the observation of an interaction, the observation of an absence of an interaction offers more of a challence since it must be decomposed into different quantities. It is particularly important to rule out the situations where $D=0 \cup X = 1 \cup L=1$, i.e. where the interaction occurred at the location but was not observed, and $D=1 \cup X = 0 \cup L =1$, when the interaction is feasible and would have been detected but did not occur at the local site. The occurrence of a true absence, our quantity of interest, corresponds to the joint event $L=0 \cup X=1 \cup D=1$, but in reality an empirical ecologist will measure the marginal probability $P(L) = k/n$ where $k$ is again the number of observed interactions and $n$ the number of observed co-occurrences.

@@

  [[Tomas suggests removing the following because it slows down procedings, Anna and Dom want it back. Shortening sounds like a good middle ground:]]
  The basic information that we are collecting consists of matrices of interaction partners. Our count of interactions between two species reflects uncertainty with respect to whether two species are capable of interacting when co-occurring at a given site ($\lambda$), chance variation in whether the interaction is realised ($\chi$),  and uncertainty with respect to whether it is detected when realised ($\delta$). In this case, what can we do to pin down any of these different types of variation?

@@

   [[Move this paragraph to intro?]] It is getting more and more common to represent interactions as probabilities in theoretical models of network structure. For example, the minimum potential model introduces gaps in the feeding niche of predators by sampling based on the likelihood of each interaction~\citep{Allesina2008}, while a gaussian probability function is used to represent the niche by~\citet{Williams2010}. \citet{Eklof2013} also introduced variability  in the computation of network dimensions, allowing the absence of interactions within the n-dimension niche of every species. Empirical investigation of trait-matching constraints often consider the occurrence of interactions as binomial process (e.g.,~\citealp{Rohr2016}). There are also ways to perform analysis of probabilistic networks, with almost all metrics having a probabilistic version~\citep{Poisot2016}. But there is not yet consensus on what an interaction probability between a pair of species means, and this is definitely a problem when comes time to estimate the uncertainty of both pairwise interactions and entire networks.

@@

      In a strict Bayesian framework, we wish to use a prior distribution that does not rely on any information from the study at hand. Network data for a similar study system may, however, not be available. In that case, one might use the first subnetwork collected as ``training data" to guide future sampling. To simulate this situation, we created priors using a single subnetwork from the middle of the geographical distribution of the~\citep{Kopelke2017} dataset (Zillis subweb). To demonstrate how the use of a data from a different system can affect the prior distribution and conclusions based on it, we repeated our analyses using priors derived from a much smaller \emph{Salix}-galler-natural enemy system~\citep{Barbour2016,Barbour2016Dryad}. This smaller system was much more densely-connected than that described in~\citet{Kopelke2017} and provided unreasonable distributions for interaction probabilities (\emph{Appendix SX}).

      To obtain the priors based on the Zillis subweb, we estimated frequencies of \emph{Salix}-galler interactions based on the normalised degree of each species in each network component (see \emph{Appendix S3} for details and code). Specifically, we obtained prior parameters of $\alpha$=8.72, $\beta$=305 for the \emph{Salix}-galler component and $\alpha$=0.700, $\beta$=8.49 for the galler-natural enemy components of the network. After calculating these prior parameters, we were then able to estimate the posterior distribution of interaction probabilities given the additional information in our dataset.

      For species where no co-occurrences were observed ($n=0$), we can calculate the estimates for the mean and variance of $\lambda_{ij}$ directly from the prior parameters following equations~\ref{mean} and~\ref{variance} (see \emph{Appendix S1} for R implementation). For the \emph{Salix}-galler network, the prior distribution  was: $\bar\lambda$=0.028, var($\lambda$)=8.60$\times$10$^{-5}$. The prior distribution for the galler-natural enemy network was: $\bar\lambda$=0.076, var($\lambda$)=0.008. The posterior interaction probabilities obtained based on the Zillis subweb were much lower than those obtained based on~\citet{Barbour2016}; this emphasises the importance of using an appropriate study system when constructing a prior (\emph{Appendix SX}).

@@

      Rather than calculating credible intervals for a posterior distribution after collecting data, we may wish to know how many data points are necessary to obtain a given level of confidence that two co-occurring species do not interact. The number of samples needed will depend on both our desired level of confidence and the threshold below which we assume that two species are unlikely to ever interact (Fig.~\ref{Salix_cdfs}; see function samples\_for\_threshold in~\emph{Appendix S1}). In our dataset, the entire 95\% credible interval was (0.013, 0.049). We may therefore be 95\% confident that the interaction probability for \emph{Salix} and galler species that have not been observed cooccurring is below 0.05. As the peak of the prior distribution for the probability of interaction between \emph{Salix} and galler probabilities is around 0.02 (Fig.~\ref{Salix_pdfs}), to be 95\% confident that the interaction probability for these species is below 0.01 would require 1029 observed co-occurrences with no interaction - far more than the number of sites in the~\citep{Kopelke2017} dataset.

      The number of samples required to be 95\% confident that the interaction probability between galler and natural enemy species is below a threshold also increases quickly as the threshold decreasesy. The 95\% credible interval is (0.0005, 0.303) for the probability of interaction between two species observed to co-occur but never interact. To be 95\% confident that the probability of interaction is below 0.1, 0.05, or 0.01 would require 15, 39, and 229 observed co-occurrances, respectively.

@@

    \indent As a case study, we use an extensively sampled \emph{Salix}-galler-natural enemy meta-network. This dataset consists of a single community type sampled across Europe: willow (\emph{Salix}) species, willow-galling sawflies, and their natural enemies. The data were collected over 29 years at 374 unique locations across Europe, with a total of 641 site visits. Each site visit can be considered as a network in its own right or as an independent sample from which to build the meta-network. The meta-network consists of 1,173 different interactions between 52 \emph{Salix} nodes, 92 herbivore nodes, and 126 natural enemy nodes. The high spatiotemporal resolution of this network and the unusually high sampling effort implemented at the site level makes this dataset particularly well suited for illustrating the difficulties in completely sampling a network and testing Bayesian approaches to overcome these difficulties.\\
    \indent We may begin by comparing the frequency of co-occurences for pairs of species in each part of the network to reveal the challenge of having sufficient sampling to be confident that an interaction does not occur. Most pairs of species (3,986/4,992 \emph{Salix}-galler pairs and  9,794/12,096 galler-natural enemy pairs) are never found co-occurring and, for species that did occur together, the total number of co-occurrences was generally low (mean=4.24, variance=36.3 for \emph{Salix}-galler pairs; mean=3.87, variance=28.8 for galler-natural enemy pairs; Fig.~\ref{histograms}A-B). The bulk of these co-occurring species pairs were never observed to interact: only 2.82\% of \emph{Salix}-galler pairs and 7.76\% of galler-natural enemy pairs were observed interacting at one or more sites. Of those pairs that did interact, the incidence of interaction was also low (mean=12.0, variance=155 for \emph{Salix}-galler pairs; mean=4.04, variance=29.3 for galler-natural enemy pairs; Fig.~\ref{histograms}C-D). Thus, even in the most extensive data set that we could find, there was very little empirical data for each species pair. This suggests that limited sampling is a major source of uncertainty in all empirical networks. This dataset also illustrates the potential for increased sampling to not necessarily reveal more interactions as a pair of species that is able to interact may not be observed interacting in all samples where the pair co-occurrs (Fig.~\ref{histograms}E-F).
  \caption{\emph{Salix} dataset}
  \label{box1}
\end{floatbox}

@@

  First, we must obtain the $\alpha$ and $\beta$ parameters for the prior distribution. In this study we obtained these parameters using the R~\citep{R} function fitdist from the package fitdistrplus~\citep{fitdistrplus}. Once $\alpha$ and $\beta$ are known, we can update them using our observed data. Specifically, we are interested in $\alpha'=\alpha+k$ and $\beta'=\beta+n-k$. These parameters can then be used to calculate a credible interval using the R~\citep{R} function qbeta. In the table below, we present the 95\% credible intervals for \emph{Salix}-galler and galler-natural enemy paris with different numbers of observed co-occurrences ($n$) and no observed interactions ($k=0$). Both sets of intervals rely on prior information derived from the Zillis subweb~\citep{Kopelke2017}.

@@

  \begin{figure}[h!]
    \caption{A simple example will illustrate the problem of imperfect detection of interactions. Assume that we want to infer the probability of an interaction between two species, $i$ and $j$. Now assume that in reality, interaction between $i$ and $j$ is completely impossible (i.e. the true $\lambda=0$) but the observer does not know this and seeks to estimate this interaction probability ($\lambda$). The number of observed interactions will follow a binomial distribution with number of interactions $k$ and number of observations $n$. Using this distribution, we can compute the credible interval of the estimated probability $\lambda$. Even assuming no added detection error in observing the incidence of the interaction, a single observation of species co-occurrence reveals very little regarding the probability of the interaction as the credible interval for a pair of species with one observation essentially spans from 0 to 1. Only with about 35 observations will the upper limit of the credible interval be lowered to 0.1. Thus, adding more observations is certainly useful in controlling uncertainty, but the number of observations added needs to be very high. Here we show the upper bound (solid black line) of a 95\% Clopper-Pearson true credible interval for $\lambda$ when $k=0$ ($i$ and $j$ have not been observed interacting) for a variety of $n$ (observed co-occurences of $i$ and $j$). A threshold interaction probability of 0.1 is indicated by the dashed red line.    }
    \label{upper_limits}
    \includegraphics*[width=.8\textwidth]{figures/upper_limit_DG.eps}
  \end{figure}

@@

      \begin{figure}[ht]
        \caption{Using prior distribution based on the \emph{Salix}-galler and galler-natural enemy networks sampled at a single site in~\citet{Kopelke2017}, we can calculate posterior distributions for the probability of interaction ($\lambda$) between two species that have not yet been observed interacting. Here we show posterior distributions for $\lambda$ in each network component ranging from the prior distribution ($n=0$ observed co-occurrence) to the distribution obtained when the pair of species has been observed co-occurring 100 times. The distribution narrows and approaches zero as the sample size increases. Likewise, the maximum likelihood estimator for the mean probability of interaction (diamonds at top of each panel) approaches zero and the 95\% credible interval (lines at top of each panel) narrows as sample size increases. \textbf{A)} The posterior distributions for $\lambda$ in the \emph{Salix}-galler component are narrower at low $n$ but shrink less with increased sampling than those for \textbf{B)} the distributions of $\lambda$ in the galler-natural enemy component.}
        \label{Salix_pdfs}
        \includegraphics*[width=.8\textwidth]{figures/Salix_Galler_pdfs_increasing_N_Zillis.eps}
        \end{figure}

      \begin{figure}[ht]
        \caption{The number of samples required to achieve a given level of confidence that an interaction probability $\lambda_{ij}$ is below a given threshold varies with both parameters. With a low threshold, our confidence that $\lambda_{ij}$ is below the threshold increases rapidly with repeated observation of co-occurrence without interaction. Here we show the cumulative density functions for threshold probabilities of 0.5 (solid line), 0.25 (dashed line), 0.1 (dash-dot line), and 0.05 (dotted line) as well as the points at which the cdf reaches 0.90 (orange square), 0.95 (red circle), and 0.975 (blue diamond) for each threshold value. The large ticks along the x-axis indicate the number of samples associated with each of these points. Note that the number of samples required to reach any given threshold is larger for \textbf{A)} the \emph{Salix}-galler network than for \textbf{B)} the galler-natural enemy network. In the galler-natural enemy network, the credible interval for a pair of species with no observed co-occurrances was 0.364. All pairs of species therefore have $\lambda$\textless0.5.}
        \label{Salix_cdfs}
        \includegraphics[width=.8\textwidth]{figures/Salix_Galler_samples_and_cdfs_Zillis.eps}

@@

    \begin{figure}[ht]
    \caption{Here we show the mean connectance, links per resource (\emph{Salix} in the \emph{Salix}-galler networks and gallers in the galler-natural enemy networks), and links per consumer for networks assembled using posterior distributions based on a single subweb in the~\citet{Kopelke2017} dataset (Zillis). We created 100 ``posterior-sampling" networks and then, for each of these, created 100 ``detection-filter" networks by randomly sampling 50\%-99\% of the interactions included in the posterior-sampling network. This simulates imperfect detection of interactions in the field. Each point represents the mean network property (e.g., connectance) obtained from a set of 100 detection-filter networks, plotted against the value of the network property in the posterior-sampling network used to create the detection-filter networks. For each property and both network types, the posterior-sampling networks cover a relatively small range of network properties than the range covered by networks with varying detection probabilities. The value of each property decreases with the proportion of links included in the detection-filter networks.}
    \label{posterior_webs}    
    \includegraphics[width=.8\textwidth]{Figures/Salix_Galler_posterior_properties_Zillis.eps}
    \end{figure}

>>>>

    Representing an assemblage of species as a network offers a convenient summary of how the community is constructed as it simultaneously accounts for species composition and interactions between species. A tabulation of the nodes (species) and their relative abundances forms the basis for traditional metrics of community composition. To move from these simpler metrics to a network framework, the tabulation of nodes is combined with interactions (links between nodes) so that networks provide additional, higher-order information on community structure. While this additional information is useful (as, for example, interactions can affect changes in species abundances over time), empirical descriptions of ecological networks are still limited because they are usually considered to be static representations of the communities and interactions they describe. That is, whether the network is assembled based on aggregated data, a single intensive ``snapshot" sample, or expert knowledge, interactions are assumed to occur deterministically wherever and whenever the community is observed~\citep{Olesen2011a}.

    The assumption of static communities contrasts significantly with the widely recognised stochasticity of ecological communities~\citep{Gotelli2000}. Community composition and species abundances vary from site to site~\citep{Baiser2012} and over time within a site~\citep{Olesen2011a}. Likewise, interactions vary over space~\citep{Kitching1987,Baiser2012}, time~\citep{Kitching1987,Olesen2011a}, and between individuals of a given species~\citep{Pires2011a,Fodrie2015,Novak2015}. Moreover, variability in community composition and interactions may or may not be closely related. The removal of a species from a site will obviously also remove its interactions but, conversely, the co-occurrence of potentially interacting species does not in itself guarantee that they will interact at a given place and time. Interactions can be lost if the interaction partners remain present but are separated in time or are too rare to detect each other~\citep{Tylianakis2010}. Interactions can also fail to occur because of environmental contingencies~\citep{Poisot2015}, or through changes to individual preferences~\citep{Fodrie2015}.

@@

    Together, the combination of these three sources of uncertainty --interaction uncertainty, process uncertainty, and detection uncertainty-- results in a range of potential explanations for the observation of an absence of interaction ($D$, $X$, and/or $L = 0$). The ecologist wanting to describe the network, however, is specifically interested in the situation where $L = 0$ (i.e., in true absences). Thus, while there is have no difficulty interpreting the observation of an interaction, the observation of an absence of an interaction offers more of a challenge since it must be decomposed into different quantities. It is particularly important to rule out the situations where $D=0 \cup X = 1 \cup L=1$, i.e. where the interaction occurred at the location but was not observed, and $D=1 \cup X = 0 \cup L =1$, when the interaction is feasible and would have been detected but did not occur at the local site. The occurrence of a true absence, our quantity of interest, corresponds to the joint event $L=0 \cup X=1 \cup D=1$, but in reality an empirical ecologist will measure the marginal probability $P(L) = k/n$ where $k$ is again the number of observed interactions and $n$ the number of observed co-occurrences.

@@

  [[Tomas suggests removing the following because it slows down proceedings, Anna and Dom want it back. Shortening sounds like a good middle ground:]]
  The basic information that we are collecting consists of matrices of interaction partners. Our count of interactions between two species reflects uncertainty with respect to whether two species are capable of interacting when co-occurring at a given site ($\lambda$), chance variation in whether the interaction is realised ($\chi$),  and uncertainty with respect to whether it is detected when realised ($\delta$). In this case, what can we do to pin down any of these different types of variation?

@@

   [[Move this paragraph to intro?]] It is getting more and more common to represent interactions as probabilities in theoretical models of network structure. For example, the minimum potential model introduces gaps in the feeding niche of predators by sampling based on the likelihood of each interaction~\citep{Allesina2008}, while a Gaussian probability function is used to represent the niche by~\citet{Williams2010}. \citet{Eklof2013} also introduced variability  in the computation of network dimensions, allowing the absence of interactions within the n-dimension niche of every species. Empirical investigation of trait-matching constraints often consider the occurrence of interactions as binomial process (e.g.,~\citealp{Rohr2016}). There are also ways to perform analysis of probabilistic networks, with almost all metrics having a probabilistic version~\citep{Poisot2016}. But there is not yet consensus on what an interaction probability between a pair of species means, and this is definitely a problem when comes time to estimate the uncertainty of both pairwise interactions and entire networks.

@@

      In a strict Bayesian framework, we wish to use a prior distribution that does not rely on any information from the study at hand. Network data for a similar study system may, however, not be available. In that case, one might use the first sub-network collected as ``training data" to guide future sampling. To simulate this situation, we created priors using a single sub-network from the middle of the geographical distribution of the~\citep{Kopelke2017} dataset (Zillis sub-network). To demonstrate how the use of a data from a different system can affect the prior distribution and conclusions based on it, we repeated our analyses using priors derived from a much smaller \emph{Salix}-galler-natural enemy system~\citep{Barbour2016,Barbour2016Dryad}. This smaller system was much more densely-connected than that described in~\citet{Kopelke2017} and provided unreasonable distributions for interaction probabilities (\emph{Appendix SX}).

      To obtain the priors based on the Zillis sub-network, we estimated frequencies of \emph{Salix}-galler interactions based on the normalised degree of each species in each network component (see \emph{Appendix S3} for details and code). Specifically, we obtained prior parameters of $\alpha$=8.72, $\beta$=305 for the \emph{Salix}-galler component and $\alpha$=0.700, $\beta$=8.49 for the galler-natural enemy components of the network. After calculating these prior parameters, we were then able to estimate the posterior distribution of interaction probabilities given the additional information in our dataset.

      For species where no co-occurrences were observed ($n=0$), we can calculate the estimates for the mean and variance of $\lambda_{ij}$ directly from the prior parameters following equations~\ref{mean} and~\ref{variance} (see \emph{Appendix S1} for R implementation). For the \emph{Salix}-galler network, the prior distribution  was: $\bar\lambda$=0.028, var($\lambda$)=8.60$\times$10$^{-5}$. The prior distribution for the galler-natural enemy network was: $\bar\lambda$=0.076, var($\lambda$)=0.008. The posterior interaction probabilities obtained based on the Zillis sub-network were much lower than those obtained based on~\citet{Barbour2016}; this emphasises the importance of using an appropriate study system when constructing a prior (\emph{Appendix SX}).

@@

      Rather than calculating credible intervals for a posterior distribution after collecting data, we may wish to know how many data points are necessary to obtain a given level of confidence that two co-occurring species do not interact. The number of samples needed will depend on both our desired level of confidence and the threshold below which we assume that two species are unlikely to ever interact (Fig.~\ref{Salix_cdfs}; see function samples\_for\_threshold in~\emph{Appendix S1}). In our dataset, the entire 95\% credible interval was (0.013, 0.049). We may therefore be 95\% confident that the interaction probability for \emph{Salix} and galler species that have not been observed co-occurring is below 0.05. As the peak of the prior distribution for the probability of interaction between \emph{Salix} and galler probabilities is around 0.02 (Fig.~\ref{Salix_pdfs}), to be 95\% confident that the interaction probability for these species is below 0.01 would require 1029 observed co-occurrences with no interaction - far more than the number of sites in the~\citep{Kopelke2017} dataset.

      The number of samples required to be 95\% confident that the interaction probability between galler and natural enemy species is below a threshold also increases quickly as the threshold decreases. The 95\% credible interval is (0.0005, 0.303) for the probability of interaction between two species observed to co-occur but never interact. To be 95\% confident that the probability of interaction is below 0.1, 0.05, or 0.01 would require 15, 39, and 229 observed co-occurrences, respectively.

@@

    \indent As a case study, we use an extensively sampled \emph{Salix}-galler-natural enemy meta-network. This dataset consists of a single community type sampled across Europe: willow (\emph{Salix}) species, willow-galling sawflies, and their natural enemies. The data were collected over 29 years at 374 unique locations across Europe with a total of 641 site visits. Each site visit or each unique site can be considered as a network in its own right or as an independent sample from which to build the meta-network. Here we take the more conservative approach and pool visits to the same site for a sample size of 374 sub-networks. The meta-network consists of 1,173 different interactions between 52 \emph{Salix} nodes, 92 herbivore nodes, and 126 natural enemy nodes. The high spatiotemporal resolution of this network and the unusually high sampling effort implemented at the site level makes this dataset particularly well suited for illustrating the difficulties in completely sampling a network and testing Bayesian approaches to overcome these difficulties.\\
    \indent We may begin by comparing the frequency of co-occurrences for pairs of species in each part of the network to reveal the challenge of having sufficient sampling to be confident that an interaction does not occur. Most pairs of species (3,986/4,992 \emph{Salix}-galler pairs and  9,794/12,096 galler-natural enemy pairs) are never found co-occurring and, for species that did occur together, the total number of co-occurrences was generally low (mean=4.24, variance=36.3 for \emph{Salix}-galler pairs; mean=3.87, variance=28.8 for galler-natural enemy pairs; Fig.~\ref{histograms}A-B). The bulk of these co-occurring species pairs were never observed to interact: only 2.82\% of \emph{Salix}-galler pairs and 7.76\% of galler-natural enemy pairs were observed interacting at one or more sites. Of those pairs that did interact, the incidence of interaction was also low (mean=12.0, variance=155 for \emph{Salix}-galler pairs; mean=4.04, variance=29.3 for galler-natural enemy pairs; Fig.~\ref{histograms}C-D). Thus, even in the most extensive data set that we could find, there was very little empirical data for each species pair. This suggests that limited sampling is a major source of uncertainty in all empirical networks. This dataset also illustrates the potential for increased sampling to not necessarily reveal more interactions as a pair of species that is able to interact may not be observed interacting in all samples where the pair co-occurs (Fig.~\ref{histograms}E-F).
  \caption{\emph{Salix} dataset}
  \label{box1}
\end{floatbox}

@@

  First, we must obtain the $\alpha$ and $\beta$ parameters for the prior distribution. In this study we obtained these parameters using the R~\citep{R} function fitdist from the package fitdistrplus~\citep{fitdistrplus}. Once $\alpha$ and $\beta$ are known, we can update them using our observed data. Specifically, we are interested in $\alpha'=\alpha+k$ and $\beta'=\beta+n-k$. These parameters can then be used to calculate a credible interval using the R~\citep{R} function qbeta. In the table below, we present the 95\% credible intervals for \emph{Salix}-galler and galler-natural enemy pairs with different numbers of observed co-occurrences ($n$) and no observed interactions ($k=0$). Both sets of intervals rely on prior information derived from the Zillis sub-network~\citep{Kopelke2017}.

@@

  \begin{figure}[h!]
    \caption{A simple example will illustrate the problem of imperfect detection of interactions. Assume that we want to infer the probability of an interaction between two species, $i$ and $j$. Now assume that in reality, interaction between $i$ and $j$ is completely impossible (i.e. the true $\lambda=0$) but the observer does not know this and seeks to estimate this interaction probability ($\lambda$). The number of observed interactions will follow a binomial distribution with number of interactions $k$ and number of observations $n$. Using this distribution, we can compute the credible interval of the estimated probability $\lambda$. Even assuming no added detection error in observing the incidence of the interaction, a single observation of species co-occurrence reveals very little regarding the probability of the interaction as the credible interval for a pair of species with one observation essentially spans from 0 to 1. Only with 35 observations will the upper limit of the credible interval be lowered to 0.1. Thus, adding more observations is certainly useful in controlling uncertainty, but the number of observations added needs to be very high. Here we show the upper bound (solid black line) of a 95\% Clopper-Pearson true credible interval for $\lambda$ when $k=0$ ($i$ and $j$ have not been observed interacting) for a variety of $n$ (observed co-occurrences of $i$ and $j$). A threshold interaction probability of 0.1 is indicated by the dashed red line.    }
    \label{upper_limits}
    \includegraphics*[width=.8\textwidth]{figures/upper_limit_DG.eps}
  \end{figure}

@@

      \begin{figure}[ht]
        \caption{Using prior distributions based on the \emph{Salix}-galler and galler-natural enemy networks sampled at a single site in~\citet{Kopelke2017}, we can calculate posterior distributions for the probability of interaction ($\lambda$) between two species that have not yet been observed interacting. Here we show posterior distributions for $\lambda$ in each network component ranging from the prior distribution ($n=0$ observed co-occurrence) to the distribution obtained when the pair of species has been observed co-occurring 100 times. The distribution narrows and approaches zero as the sample size increases. Likewise, the maximum likelihood estimator for the mean probability of interaction (diamonds at top of each panel) approaches zero and the 95\% credible interval (lines at top of each panel) narrows as sample size increases. \textbf{A)} The posterior distributions for $\lambda$ in the \emph{Salix}-galler component are narrower at low $n$ but shrink less with increased sampling than those for \textbf{B)} the distributions of $\lambda$ in the galler-natural enemy component.}
        \label{Salix_pdfs}
        \includegraphics*[width=.8\textwidth]{figures/Salix_Galler_pdfs_increasing_N_Zillis.eps}
        \end{figure}

      \begin{figure}[ht]
        \caption{The number of samples required to achieve a given level of confidence that an interaction probability $\lambda_{ij}$ is below a given threshold varies with both parameters. With a low threshold, our confidence that $\lambda_{ij}$ is below the threshold increases rapidly with repeated observation of co-occurrence without interaction. Here we show the cumulative density functions for threshold probabilities of 0.5 (solid line), 0.25 (dashed line), 0.1 (dash-dot line), and 0.05 (dotted line) as well as the points at which the cdf reaches 0.90 (orange square), 0.95 (red circle), and 0.975 (blue diamond) for each threshold value. The large ticks along the x-axis indicate the number of samples associated with each of these points. \textbf{A)} In the \emph{Salix}-galler network component, the 95\% credible interval for $\lambda$ when $n$=0 was (0.013, 0.049). We can therefore be at least 95\% confident that $\lambda$ is below thresholds of 0.1 or 0.05 without any observed co-occurrence. To be confident that $\lambda$ is less than 0.01, however, would require more observed co-occurrences than there are sites in our dataset. \textbf{B)} In the galler-parasitoid network component, the 95\% credible interval for $\lambda$ was substantially broader and many observed co-occurrences (\approx 15-35) are required to be 95\% confident that $\lambda$ is below thresholds of 0.1 or 0.05.}
        \label{Salix_cdfs}
        \includegraphics[width=.8\textwidth]{figures/Salix_Galler_samples_and_cdfs_Zillis.eps}

@@

    \begin{figure}[ht]
    \caption{Here we show the mean connectance, links per resource (\emph{Salix} in the \emph{Salix}-galler networks and gallers in the galler-natural enemy networks), links per consumer, and nestedness (NODF) for networks assembled using posterior distributions based on a single sub-network in the~\citet{Kopelke2017} dataset (Zillis). We created 100 ``posterior-sampling" networks and then, for each of these, created 100 ``detection-filter" networks by randomly sampling 50\%-99\% of the interactions included in the posterior-sampling network. This simulates imperfect detection of interactions in the field. Each point represents the mean network property (e.g., connectance) obtained from a set of 100 detection-filter networks, plotted against the value of the network property in the posterior-sampling network used to create the detection-filter networks. For each property and both network types, the posterior-sampling networks cover a relatively small range of network properties than the range covered by networks with varying detection probabilities. The value of each property decreases with the proportion of links included in the detection-filter networks.}
    \label{posterior_webs}    
    \includegraphics[width=.8\textwidth]{Figures/Salix_Galler_posterior_properties_Zillis.eps}
    \end{figure}
